\sc Cells at War: The Playfulness of Game-Based Learning

### 2023-04-04 thesis_template/paper0904.tex
started writing discussion

\documentclass{article}
%\documentclass[twocolumn]{article}
%\documentclass[onecolumn]{article}
% \usepackage{scrtime} % for \thistime (this package MUST be listed first!)
\DeclareUnicodeCharacter{0301}{\'{e}}
\usepackage{float}
\usepackage{times}
\usepackage{graphicx}
\usepackage{float}
\usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{caption}
\usepackage{notoccite}
\usepackage{pgfplotstable}
%\usepackage[round]{natbib}
%\setcitestyle{aysep={}} %removes the comma between the author and year in citations
%\usepackage{underscore}
\usepackage{pdfpages}
\usepackage{xcolor,colortbl}%for changing cell colour
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{capt-of}
\pagestyle{fancy}
\setlength{\headheight}{15.2pt}
\setlength{\headsep}{13 pt}
\setlength{\parindent}{28 pt}
\setlength{\parskip}{12 pt}
\pagestyle{fancyplain}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
% \usepackage{color,amsmath,amssymb,amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{xspace}
\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc, arrows}
\usetikzlibrary{external}
\usepackage{pgfplots}
\pgfplotsset{layers/my layer set/.define layer set={background,main,foreground}{},
        set layers=my layer set,}

@@

Concept development began in September of 2021. In this phase, students from both institutions worked collaboratively to brainstorm concepts for a biological video game that would be both engaging and educational. The theme for the game was centred around single-gene diseases. Biology students from McMaster University were responsible for selecting and researching a specific single-gene disease. This information was exchanged with students from George Brown College, who in-turn provided a wealth of knowledge on how to turn these static, difficult to understand concepts into engaging gameplay mechanics. Students pitched these proposals to supervising professors who then selected the ideas and game elements that best suited the goals of the project.

@@

The survey was developed and delivered through the LimeSurvey\textregistered \space platform. Students were asked a total of 14 questions regarding opinions and attitudes on their current undergraduate education, as well as feedback on game-based learning in the biology classroom. The National Survey of Student Engagement (NSSE) was used as a framework to generate the questions that were asked. NSSE questions assess the extent to which students engage in educational practices in the context of higher levels of learning (NSSE website citation). MORE HERE ABOUT NSSE...

@@

\section{Discussion}

We need to highlight in this section the use of Cells at War as an instructional tool as well as the benefits that students get out of this work integrated learning experience

>>>>

\documentclass[10pt]{article}
%\documentclass[twocolumn]{article}
%\documentclass[onecolumn]{article}
% \usepackage{scrtime} % for \thistime (this package MUST be listed first!)
\DeclareUnicodeCharacter{0301}{\'{e}}
\usepackage{float}
\usepackage{times}
\usepackage{graphicx}
\usepackage{float}
\usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{caption}
\usepackage{notoccite}
\usepackage{pgfplotstable}
%\usepackage[round]{natbib}
%\setcitestyle{aysep={}} %removes the comma between the author and year in citations
%\usepackage{underscore}
\usepackage{pdfpages}
\usepackage{xcolor,colortbl}%for changing cell colour
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{capt-of}
\pagestyle{fancy}
\setlength{\headheight}{15.2pt}
\setlength{\headsep}{13 pt}
\setlength{\parindent}{28 pt}
\setlength{\parskip}{12 pt}
\pagestyle{fancyplain}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
% \usepackage{color,amsmath,amssymb,amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{xspace}
\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc, arrows}
\usetikzlibrary{external}
\usepackage{pgfplots}
\pgfplotsset{layers/my layer set/.define layer set={background,main,foreground}{},
        set layers=my layer set,}

@@

Concept development began in September of 2021. In this phase, students from both institutions worked collaboratively to brainstorm concepts for a biological video game that would be both engaging and educational. The theme for the game was centred around single-gene diseases. Biology students from McMaster University were responsible for selecting and researching a specific single-gene disease. This information was exchanged with students from George Brown College, who in-turn provided a wealth of knowledge on how to turn these static, difficult to understand concepts into engaging gameplay mechanics. Students pitched these proposals to supervising professors who then selected the ideas and game elements that best suited the goals of the project. The disease that was selected was Pompe disease, a rare genetic disease that causes skeletal and cardiac muscle weakness due to the accumulation of glycogen within lysosomes. The game envisioned was a shooter type game, where students would be tasked with shooting enzymes to break down glycogen into glucose in order to remove glycogen from the lysosomes. Each level highlighted a different stage of the disease; a healthy individual, early onset pompe disease individual, and full fledged pompe disease individual. Through each level, students would be able to see the effects of having less enzymes to break down glycogen.

@@

The survey was developed and delivered through the LimeSurvey\textregistered \space platform. Students were asked a total of 14 questions regarding opinions and attitudes on their current undergraduate education, as well as feedback on game-based learning in the biology classroom. The National Survey of Student Engagement (NSSE) was used as a framework to generate the questions that were asked. NSSE questions assess the extent to which students engage in educational practices in the context of higher levels of learning (NSSE website citation). MORE HERE ABOUT NSSE...
\newpage

@@

%We need to highlight in this section the use of Cells at War as an instructional tool as well as the benefits that students get out of this work integrated learning experience
\section{Discussion}

This project has developed an educational video game focused on a single gene disease, which presents students with important cellular and molecular biology concepts in an engaging and interactive manner. Through this study, we have found a way to supplement lecture material with a video game, and examined the impact of game-based learning on student motivation and engagement. This study also shows the immense benefits both students and faculty gain when engaging in a collaborative and interdisciplinary work-integrated learning experience.

\subsection{Student benefits of game-based learning}

\subsection{Benefits of the game-design process for educators and students}
